BLAST: Block Applications for Things

### 2022-03-07 demo-eswc22/paper.tex
minor fixes

The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
For execution, the editor generates JavaScript code that can be executed in the browser.
The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices the use the BLE GAP and GATT profiles as well as the USB Human Interface Devices (HID) interface.
The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
In addition, the system includes access to the camera and sound output via browser APIs using the WoT interface.
Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
The ability to issue HTTP requests is implemented using the @@@ API, Social Linked Data (Solid) authentication is implemented using the @@@ API, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
Next the the presented scenario around geofences, we have also implemented a BLAST program to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.

>>>>

The editor uses the Blockly library and provides custom control and command blocks that make up the BLAST language.
For execution, the editor generates JavaScript code that can be executed in the browser.
The system builds on the Web Bluetooth API\footnote{\url{https://webbluetoothcg.github.io/web-bluetooth/}} and the WebHID API\footnote{\url{https://wicg.github.io/webhid/}} to interact with devices.
The system uses the Web of Things abstraction as interface; we have implemented the WoT interface for eight devices the use the BLE GAP and GATT profiles as well as the USB Human Interface Devices (HID) interface.
The WoT interface contains the metadata and interaction affordances as well as the JavaScript code needed for communication.
In addition, the system includes access to the camera and sound output via browser APIs using the WoT interface.
Further, the system includes access to the Web Speech API\footnote{\url{https://wicg.github.io/speech-api/}}.
The functionality to issue HTTP requests is implemented using the @@@ API/library, Social Linked Data (Solid) authentication is implemented using the @@@ library, and SPARQL query support is implemented using µRDF.js\footnote{\url{https://github.com/vcharpenay/uRDF.js/}}.
Next to the presented small scenario around geofences, we have also developed BLAST programs to control and monitor an automated picking line to prepare orders in a more complex logistics scenario.
